A Comparison of Graph Processing Systems

### 2020-09-28 documentation/paper/sections/testingMethods.tex
umbenennen der environment zu testing environment

\subsubsection{Environment}
For testing the graph processing systems, we used 5 machines with two AMD EPYC 7401 (24-Cores) and 256 GB of RAM each. Thus, each machine has 96 cores, half of which are virtual. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All five machines were running Ubuntu 18.04.2 LTS.

>>>>

\subsubsection{Testing Environment}
For testing the graph processing systems, we used 5 machines with two AMD EPYC 7401 (24-Cores) and 256 GB of RAM each. Thus, each machine has 96 cores, half of which are virtual. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All five machines were running Ubuntu 18.04.2 LTS.
